\documentclass[11pt]{article}
\usepackage{hyperref}
\usepackage{fullpage}
\usepackage{color}
\usepackage{titlesec}

\titleformat{\section}
{\normalfont\normalsize\bfseries }
{}{0em}{\MakeUppercase}

\titleformat{\subsection}
{\normalfont\normalsize\bfseries}
{}{0em}{}

\title{\vspace{-50px}Curriculum Vitae\vspace{-45px}}

\date{}
\begin{document}
\maketitle

\begin{tabular}{lll}
  \textbf{Harley Eades III, Ph.D.}\\
  Assistant Professor\\
  School of Computer and Cyber Sciences\\
  1120 15th Street, Allgood Hall E132\\
  Augusta, GA 30912\\
  706-667-4543 (office)\\
  217-358-6999 (mobile)\\
  \href{mailto:heades@augusta.edu}{heades@augusta.edu} (office)\\
  \href{mailto:harley.eades@gmail.com}{harley.eades@gmail.com} (personal)\\  
  \url{http://www.metatheorem.org}\\
\end{tabular}

\section{Education:}
\begin{itemize}
\item[] \textbf{Doctor of Philosophy in Computer Science}, August 2014.\\
  \begin{tabular}{lll}
    \emph{University of Iowa, IA}\\
    Dissertation Title: The Semantic Analysis of Advanced Programming Languages
  \end{tabular}

\item[] \textbf{Masters of Science in Computer Science}, May 2013.\\
  \begin{tabular}{lll}
    \emph{University of Iowa, IA}\\
  \end{tabular}

\item[] \textbf{Bachelor of Science in Applied Mathematics and Computer Science}, May 2009.\\
  \begin{tabular}{lll}
    \emph{Millikin University}\\
  \end{tabular}    
\end{itemize}

  
  %% \subsection{Additional Education} 
  %% \begin{itemize}
  %% \item[] JAIST Spring School: Formal Reasoning: Theory and Application, JAIST, Kanazawa, Japan, March 2012.

  %% \item[] Oregon Programming Languages Summer School, University of Oregon, Eugene, OR., July 2011.
  %% \end{itemize}

\section{Work Experience:}
\label{sec:work_experience:}
\begin{itemize}
\item[] 2014, August -- Present: Assistant Professor\vspace{-10px}
\item[] Augusta University School of Computer and Cyber Sciences
  \vspace{-10px}
  \begin{itemize}
  \item[$\bullet$] Research, teaching, service
  \end{itemize}
\end{itemize}
% section work_experience: (end)

\section{Awards/Recognition:}
\label{sec:awards/recognition}
\begin{itemize}\itemsep-2px
\item Recognized for Scholarship at the Annual Celebration of Faculty, Augusta University, 2018.
\item The Graduate College Summer Fellowship, University of Iowa, 2013.
  
\item The Strategic Initiative Funds Fellowship, University of Iowa, 2011.
  
\item Mathematics and Computer Science Award, Millikin University, 2009.  
  
\item Mathematics and Computer Science Award, Millikin University, 2008.  
  
\item Mathematics and Computer Science Award, Millikin University, 2007.
\end{itemize}
% section awards/recognition (end)

\section{Professional Organization Memberships:}
\label{sec:memberships}
\begin{itemize}\itemsep-2px
\item ACM Special Interest Group on Logic and Computation (2014--Present) 
\item ACM Special Interest Group on Programming Languages (2014--Present)  
\item Eurpoean Association of Theoretical Computer Science (2011--Present)
\end{itemize}
% section memberships (end)

\section{National and International Service:}
\label{sec:national_and_international_service:}
\begin{itemize}\itemsep-2px
  \item Chair (2019--2020), First Annual Southeast Regional Programming Languages Seminar (SERPL).
  \item Programming Committee Member (2017--Present), The International Workshop on Graphical Models for Security (GraMSec). 
  \item Programming Committee Member (2013), The Seventh ACM SIGPLAN Workshop on Programming Languages meets Program Verification (PLPV).
  \item Reviewer (2019), NSF Hardware and Software Foundations SMALL competition.
  \item Reviewer (2019), NSF Formal Methods in the Field (FMitF) competition,
  \item Reviewer (2018), 11th Conference on Intelligent Computer Mathematics (CICM 2018).
  \item Reviewer (2018), Advances in Modal Logic (AiML).
  \item Reviewer (2018), Seventh Workshop on Mathematically Structured Functional Programming (MSFP).
  \item Reviewer (2018), Logical Methods in Computer Science (Journal).
  \item Reviewer (2016), Sixteenth International Workshop on Logic and Computational Complexity (LCC).
  \item Reviewer (2016), Advances in Modal Logic (AiML).
  \item Reviewer (2016), The Thirty-First Annual ACM/IEEE Symposium on Logic in Computer Science (LICS).
  \item Reviewer (2015), Workshop on Logic, Language, Information and Computation (Wollic).          
  \item Reviewer (2015), Logica Universalis (Journal).    
  \item Reviewer (2015), The 13th International Conference on Typed Lambda Calculi and Applications (TLCA).    
  \item Reviewer (2015), Logical Methods in Computer Science (Journal).    
  \item Reviewer (2014), The 7th International Joint Conference on Automated Reasoning (IJCAR).
  \item Reviewer (2014), Joint Meeting of the Twenty-Third EACSL Annual Conference on Computer Science Logic (CSL) and the Twenty-Ninth Annual ACM/IEEE Symposium on Logic in Computer Science (LICS).
  \item Reviewer (2013), Logical Methods in Computer Science (Journal).    
  \item Reviewer (2013), The 11th International Conference on Typed Lambda Calculi and Applications (TLCA).
  \item Reviewer (2013), The 19th International Conference on Tools and Algorithms for the Construction and Analysis of Systems (TACAS).  
  \item Reviewer (2013), The 23rd International Conference on Rewriting Techniques and Applications (RTA).
  \item Reviewer (2012), The 6th International Joint Conference on Automated Reasoning (IJCAR).
  \end{itemize}
% section national_and_international_service: (end)

\section{University/College Service:}
\label{sec:universitycollege_service:}
\begin{itemize}
\item Member of the Graduate School of Augusta University (Spring 2019 -- Present)
\item SCCS Masters in Computer Science Proposal Committee (Spring 2019)
\item SCCS Faculty Search (Spring 2019)
\item SCCS Faculty Affairs Committee (2018)
\item CURS Faculty Advisory Committee (2017--Present)
\item S-STEM Workgroup (2017--2018)
\item CS Education Endorsement Workgroup (2017--2018)
\item SCCS Faculty Affairs Committee, Augusta University (2017--Present)
\item IT Advisory Committee: Research Advisory Subcommittee (2016--Present)
\item Curriculum and Academic Policies Augusta University, (2016--2018)
\item HULL Faculty Affairs Committee (2016--2017)
\item HULL ABET Assessment Committee (2015--2017)
\item HULL Computer Science Curriculum Committee (2015)
\item HULL Undergraduate Curriculum Committee, Augusta University (Fall 2015)
\item Internal Advisory Committee for the Cyber Institute (2014--2016)
\end{itemize}
% section university/college_service: (end)


\section{Teaching Experience:}
\label{sec:teaching_experience:}
\begin{itemize}
\item Mathematical Structures in Computer Science (Undergraduate)
\item Theory of Computation (Undergraduate)
\item Programming Languages Concepts (Undergraduate)  
\item Introduction to Category Theory in Computer Science (Graduate)
\end{itemize}
% section teaching_experience: (end)

  %% \item[] \textbf{Students Supervised (AU)}\\
  %% \item[] 
  %%   \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|l|}
  %%   \hline
  %%   \textbf{Standing} & \textbf{Student Name} & \textbf{Years} & \textbf{Outcome}\\  
  %%   \hline
  %%   Undergraduate     & Blake Watkins         & Summer 2018 - Present     & ongoing\\
  %%                     & Aubrey Bryant         & Fall 2017   - Present     & ongoing\\
  %%                     & Preston Keel          & Fall 2017   - Present     & ongoing\\
  %%                     & Gisela Font-Sayers    & Fall 2016   - Spring 2017 & masters student U. Nebraska-Lincoln\\
  %%                     & Michael Townsend      & Summer 2016 - Fall 2017   & masters students Georgia Tech\\
  %%                     & Matthew Tennis        & Summer 2016 - Spring 2017 & graduated\\
  %%                     & Chad Reynolds         & Spring 2014 - Spring 2015 & graduated\\
  %%   \hline
  %%   \end{tabular}
  %% \item[] \textbf{Visiting Graduate Students Supervised}\\
  %% \item[]
  %%   {\small
  %%   \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|l|}
  %%   \hline
  %%   \textbf{Standing} & \textbf{Student Name} & \textbf{Time}\\  
  %%   \hline
  %%   Tulane University, Ph.D. Program in Mathematics                       & Nathan Bedell       & Summer 2018 - Present\\
  %%   North Carolina State University, Ph.D. Program in Computer Science    & Jiaming Jiang       & Summer 2016 - Fall 2017\\
  %%   University of Iowa, Ph.D. Program in Computer Science                 & Richard Blair       & Summer 2017\\
  %%   \hline
  %%   \end{tabular}
  %%   }
  %% \end{itemize}
  
  
  \section{Refereed Journal Publications}
  \begin{enumerate}
  \item[] \textbf{Constructive Temporal Logic, Categorically.} Valeria
    de Paiva and Harley Eades III.  IFCoLog Journal of Logic and its
    Applications. 01 February 2017. Volume 4, Number 4, Special Issue
    Dedicated to the Memory of Grigori Mints.  21 pages in length.

  \item[] \textbf{Dualized Simple Type Theory.} Harley D. Eades III, Aaron
    Stump, Ryan McCleeary. Logical Methods in Computer Science, 15
    August 2016. Volume 12, Issue 3. 47 pages in length.
    DOI: 10.2168/LMCS-12(3:2)2016    

  \item[] \textbf{Equational Reasoning about Programs with General
    Recursion and Call-by-value Semantics}.  Garrin Kimmell, Aaron
    Stump, Harley D. Eades III, Peng Fu, Tim Sheard, Stephanie Weirich,
    Chris Casinghino, Vilhelm Sjoberg, Nathan Collins and Ki Yung Ahn.
    Special Issue on Advanced Programming Techniques for Construction of
    Robust, General and Evolutionary Programs. Progress in Informatics,
    pages 19-46, March 2013, journal version of PLPV’12 paper.

  \end{enumerate}

  \section{Refereed Conference and Workshop Publications}
  \label{subsec:symposium_publications}
  \begin{enumerate}

  \item[] \textbf{On the Lambek Calculus with an Exchange Modality.}
    Jiaming Jiang, Harley Eades III, and Valeria de Paiva. To appear
    in the Proceedings of The Joint Workshop on Linearity \& TLLA,
    co-located with Third International Conference on Formal
    Structures for Computation and Deduction (FCSD) in conjunction
    with the Federated Logic Conference. 48 pages in length.
    
  \item[] \textbf{On Linear Logic, Functional Programming, and Attack
    Trees}. Harley Eades III, Jiaming Jiang, and Aubrey Bryant. In:
    Cybenko G., Pym D., Fila B. (eds) Graphical Models for
    Security. GraMSec 2018. Lecture Notes in Computer Science, vol
    11086. Springer, Cham. DOI: 10.1007/978-3-030-15465-3\_5. 15 pages
    in length.

  \item[] \textbf{Extended Abstract: On the Lambek Calculus with an
    Exchange Modality.}  Jiaming Jiang, Harley Eades III, and Valeria
    de Paiva. The Joint Workshop on Linearity \& TLLA, co-located with
    Third International Conference on Formal Structures for
    Computation and Deduction (FCSD) in conjunction with the Federated
    Logic Conference. July 2018. 8 pages in length.
    
  \item[] \textbf{Dialectica Categories for the Lambek Calculus.}
    Valeria de Paiva and Harley Eades III. In In Sergei Artemov and
    Anil Nerode, editors, Proceedings of the Symposium of Logical
    Foundations of Computer Science (LFCS), Deerfield Beach, Florida,
    United States, Jan. 8-11, volume 1073 of Lecture Notes in Computer
    Science, pages 256-272. Springer International Publishing,
    2018. DOI: 10.1007/978-3-319-72056-2\_16.  Acceptance rate: 56\%.    
    
  \item[] \textbf{Extended Abstract: Explaining Type Errors}.  Brent
    Yorgey, Richard A. Eisenberg, and Harley D. Eades III. Off the
    Beaten Track (OBT). Associated with The 45th ACM SIGPLAN Symposium
    on Principles of Programming Languages (POPL). January 2018. 2
    pages in length.
       
  \item[] \textbf{Introducing a New Project on The Combination of
    Substructural Logics and Dependent Type Theory.} Harley Eades III.
    International Workshop on Trends in Linear Logic and Applications
    (TLLA) affiliated with the Second International Conference on
    Formal Structures for Computation and Deduction (FSCD). 31 July
    2017. 2 pages in length.
    
  \item[] \textbf{Abstract: Dialectica categories for the Lambek
    calculus}.  Valeria de Paiva and Harley D. Eades III. Association for
    Symbolic Logic (ASL) Spring Meeting jointly held with the Annual
    Meeting of the Pacific Division of the American Philosophical
    Association.  April 2017.  2 pages in length.    
    
  \item[] \textbf{Abstract: On Linear Modalities for Exchange,
    Weakening, and Contraction}.  Harley D. Eades III and Jiaming Jiang.
    Workshop on Linear Logic, Mathematics, and Computer
    Science. Associated with Linear Logic: Interaction, Proofs, and
    Computation (LL2016).  November 2016. 2 pages in length.

  \item[] \textbf{Multiple Conclusion Linear Logic: Cut Elimination and
    More}.  Harley D. Eades III and Valeria de Paiva. In Sergei Artemov
    and Anil Nerode, editors, Proceedings of the Symposium of Logical
    Foundations of Computer Science (LFCS), Deerfield Beach, Florida,
    United States, Jan. 4-7, volume 9537 of Lecture Notes in Computer
    Science, pages 90-105. Springer International Publishing,
    2016. DOI: 10.1007/978-3-319-27683-0\_7.  Acceptance rate: 57\%.

  \item[] \textbf{Full Intuitionistic Linear Logic (FILL).} Harley
    D. Eades III and Valeria de Paiva. Entry in Encyclopedia of Proof
    Systems. Presented as a Poster at the 25th jubilee edition of the
    International Conference on Automated Deduction
    (CADE). \url{http://proofsystem.github.io/Encyclopedia/}. 2015.
    
  \item[] \textbf{Extended Abstract: Reconsidering Intuitionistic
    Duality}.  Aaron Stump, Harley D. Eades III, and Ryan
    McCleeary. Workshop on Control Operators and their Semantics
    (COS).  Affiliated with Rewriting, Deduction, and Programming
    (RDP). June 2013.  5 pages in length.

  \item[] \textbf{Hereditary Substitution for the
    $\lambda\Delta$-Calculus}.  Harley D. Eades III and Aaron Stump.
    In Ugo de'Liguoro and Alexis Saurin, editors, Proceedings First
    Workshop on Control Operators and their Semantics, Eindhoven, The
    Netherlands, June 24-25, 2013 , volume 127 of Electronic
    Proceedings in Theoretical Computer Science, pages 45-65. Open
    Publishing Association, 2013.

  \item[] \textbf{LFSC for SMT Proofs: Work in Progress}.  Aaron
    Stump, Andrew Reynolds, Cesare Tinelli, Austin Laugesen, Harley
    D. Eades III, Corey Oliver and Ruoyu Zhang.  Proof Exchange For
    Theorem Proving (PxTP). 2012. 7 pages in length.
    
  \item[] \textbf{Irrelevance, heterogeneous equality, and call-by-value
    dependent type systems}.  Vilhelm Sjoberg, Chris Casinghino, Ki
    Yung Ahn, Nathan Collins, Harley D. Eades III, Peng Fu, Garrin
    Kimmell, Tim Sheard, Aaron Stump, and Stephaine Weirich.  In
    J. Chapman and P. B. Levy, editors, Proceedings Fourth Workshop on
    Mathematically Structured Functional Programming, Tallinn,
    Estonia, 25 March 2012, volume 76 of Electronic Proceedings in
    Theoretical Computer Science, pages 112-162. Open Publishing
    Association, 2012.
    
  \item[] \textbf{Equational Reasoning about Programs with General
    Recursion and Call-by-value Semantics}.  Garrin Kimmell, Aaron
    Stump, Harley D. Eades III, Peng Fu, Tim Sheard, Stephanie
    Weirich, Chris Casinghino, Vilhelm Sjoberg, Nathan Collins and Ki
    Yung Ahn.  The Sixth ACM SIGPLAN Workshop Programming Languages
    meets Program Verification (PLPV), pages 15-26, 2012.
    
  \item[] \textbf{Hereditary Substitution for Stratified System
    F}. Harley D. Eades III and Aaron Stump.  International Workshop
    on Proof-Search in Type Theories (PSTT), 2010. Affiliated with the
    Federated Logic Conference (FLoC). 7 pages in length.    
  \end{enumerate}

  %% \subsection{Workshop Talks}
  %% \begin{enumerate}        
  %%   \item \textbf{Dualized Type Theory.} Harley D. Eades III.
  %%     Fifth International Workshop on Classical Logic and Computation (CL\&C). July 2014. Affiliated with
  %%     CSL-LICS 2014. Length: 20min.
      
  %%   \item \textbf{On the Categorical Structure of Bi-Intuitionistic Logics}. Harley D. Eades III.
  %%     The University of Iowa Mini-Symposium. October 2013. Length: 30min.
      
  %%   \item \textbf{The Categorical Structure of Semi-Bilinear Intuitionistic Logic}. Harley D. Eades III.
  %%     Midwest Verification Day. September 2013. Length: 20min.
      
  %%   \item \textbf{Hereditary Substitution for the $\lambda\Delta$-Calculus}. Harley D. Eades III. 
  %%     Workshop on Control Operators and their Semantics (COS). 
  %%     Affiliated with Rewriting, Deduction, and Programming (RDP). June 2013. Length: 20min.
      
  %%   \item \textbf{Hereditary Substitution for the }$\lambda\Delta$\textbf{-Calculus}. Harley D. Eades III.
  %%     Midwest Verification Day. September 2012. Length: 20min.
      
  %%   \item \textbf{Hereditary Substitution for the }$\lambda\Delta$\textbf{-Calculus}. Harley D. Eades III.
  %%     Fourth International Workshop on Classical Logic and Computation (CL\&C). July 2012. Affiliated with ICALP 2012.
  %%     Length: 20min.
      
  %%   \item \textbf{Separation of Proof from Program}.
  %%     Harley D. Eades III. Midwest Verification Day. September 2011. Length: 20min.

  %%   \item \textbf{Exploring the Reach of Hereditary Substitution}. Harley D. Eades III.
  %%     Types for Proofs and Programs (TYPES). 2011. Length: 30min.
      
  %%   \item \textbf{Hereditary Substitution for Stratified System F}. Harley D. Eades III. 
  %%     International Workshop on Proof-Search in Type Theories (PSTT). July 2010. Length: 20min.
  %%   \end{enumerate}

  \section{Invited Speaker Presentations}
    \label{subsec:invited_speaker}
    \begin{enumerate}
    \item[] \textbf{The Three Perspectives of Computation.} Harley
      D. Eades III. Department of Mathematical Sciences Colloquium
      Speaker. October 2016. Length: 55min.
      
    \item[] \textbf{A New Foundation of Attack Trees in Monoidal
      Categories}. Harley D. Eades III. Computer Science Department
      Colloquium Speaker.  The University of Iowa. September
      2016. Length: 60min.      
    \end{enumerate}
    % subsection invited_speaker (end)
    
    %% \subsection{Undergraduate Research Publications}
    %% \begin{enumerate}
    %%   \item   \textbf{Zero-Divisors and Their Graph Languages}. Harley D. Eades III. Rose-Hulman Undergraduate 
    %%     Mathematics Journal. Vol. 10, Issue 2, 2009. 
    %% \end{enumerate}

    \section{Other Research Contributions}
    \label{subsec:other_work}
    \begin{enumerate}      
    \item[] \textbf{Lambek Calculus.} Harley D. Eades III and Valeria de
      Paiva. Entry in Encyclopedia of Proof
      Systems. \url{http://proofsystem.github.io/Encyclopedia/}. 2016.

    \item[] \textbf{Two-sided Linear Sequent Calculus.} Elaine Pimentel and Harley D. Eades III. Entry in Encyclopedia of Proof Systems. \url{http://proofsystem.github.io/Encyclopedia/}. 2015.

    \item[] \textbf{Constructive Modal Logic S4 (CS4).} Harley D. Eades III and Valeria de Paiva. Entry in Encyclopedia of Proof Systems. \url{http://proofsystem.github.io/Encyclopedia/}. 2015.

    \item[] \textbf{Full Intuitionistic Logic.} Harley D. Eades III and Valeria de Paiva. Entry in Encyclopedia of Proof Systems. \url{http://proofsystem.github.io/Encyclopedia/}. 2015.
    \end{enumerate}
    % subsection other_work (end)

    \section{Grants/Funding}
    \label{subsec:funding_(awarded_grants)}
    \vspace{-10px}
    \begin{tabular}{l}
      Percent Funded: 43\%\\
      Total Funded: \$84,484\\
      \begin{tabular}{|l|l|l|}
          \hline
          \textbf{Title} & CAREER: Developing the Theory of Resource-\\
                         & Sensitive Type Systems \\
          \hline
          \textbf{Funding Organization} & National Science Foundation (NSF)\\
          \hline
          \textbf{\$ Amount Requested} & \$550,000\\
          \hline
          \textbf{Type} & External\\
          \hline
          \textbf{PI(s)} & Harley Eades III\\
          \hline
          \textbf{Beginning/Ending Dates} & March 2020 - February 2025\\
          \hline
          \textbf{Status} (Unfunded, Funded, Pending) & Pending\\
          \hline
        \end{tabular}\\
        \\
        \begin{tabular}{|l|l|l|}
          \hline
          \textbf{Title} & NSF Student Travel Grant for 2019 Southeast\,\,\,\\
          & Regional Programming Languages Seminar \\
          & (SERPL)\\
          \hline
          \textbf{Funding Organization} & National Science Foundation (NSF)\\
          \hline
          \textbf{\$ Amount Requested} & \$5,000\\
          \hline
          \textbf{Type} & External\\
          \hline
          \textbf{PI(s)} & Harley Eades III and Cl\'ement Aubert\\
          \hline
          \textbf{Beginning/Ending Dates} & March 2019 - February 2020\\
          \hline
          \textbf{Status} (Unfunded, Funded, Pending) & Funded\\
          \hline
        \end{tabular}\\
        \\
        \begin{tabular}{|l|l|l|}
          \hline
          \textbf{Title} & CAREER: Developing the Theory of Resource-\\
                         & Sensitive Dependent Type Systems \\
          \hline
          \textbf{Funding Organization} & National Science Foundation (NSF)\\
          \hline
          \textbf{\$ Amount Requested} & \$642,591\\
          \hline
          \textbf{Type} & External\\
          \hline
          \textbf{PI(s)} & Harley Eades III\\
          \hline
          \textbf{Status} (Unfunded, Funded, Pending) & Unfunded\\
          \hline
        \end{tabular}\\
        \\        
    \end{tabular}
    \\
    \begin{tabular}{l}
      \begin{tabular}{|l|l|l|}
          \hline
          \textbf{Title} & IIAP: Verifying Information Flow Secure \,\,\,\,\,\,\,\,\,\,\,\,\,\,\, \\
          & Programs using Graded Dependent Types\\
          \hline
          \textbf{Funding Organization} & Augusta University's Cyber Institute\\
          \hline
          \textbf{\$ Amount Requested} & \$9,263\\
          \hline
          \textbf{Type} & Internal\\
          \hline
          \textbf{PI(s)} & Harley Eades III\\
          \hline
          \textbf{Beginning/Ending Dates} & November 2017 - July 2018\\
          \hline
          \textbf{Status} (Unfunded, Funded, Pending) & Funded\\
          \hline
        \end{tabular}\\
        \\        
      \begin{tabular}{|l|l|l|}
          \hline
          \textbf{Title} & CAREER: Tenli: A Platform that Takes the\,\,\,\,\,\,\, \\
          & Verification of Resource Dependent Systems \\
          & Seriously\\
          \hline
          \textbf{Funding Organization} & National Science Foundation (NSF)\\
          \hline
          \textbf{\$ Amount Requested} & \$500,272\\
          \hline
          \textbf{Type} & External\\
          \hline
          \textbf{PI(s)} & Harley Eades III\\
          \hline
          \textbf{Status} (Unfunded, Funded, Pending) & Unfunded\\
          \hline
        \end{tabular}\\
        \\        
      \begin{tabular}{|l|l|l|}
          \hline
          \textbf{Title} & Disco: A Programming Environment for \,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\\
          & Discrete Mathematics Education \\
          \hline
          \textbf{Funding Organization} & National Science Foundation (NSF)\\
          \hline
          \textbf{\$ Amount Requested} & \$299,254\\
          \hline
          \textbf{Type} & External (Collaborative)\\
          \hline
          \textbf{PI(s)} & Harley Eades III and Brent Yorgey\\
          \hline
          \textbf{Status} (Unfunded, Funded, Pending) & Unfunded\\
          \hline
        \end{tabular}\\
        \\
      \begin{tabular}{|l|l|l|}
          \hline
          \textbf{Title} & CRII:SHF: A New Foundation for Attack \,\,\,\,\,\,\,\,\,\,\,\,\,\\
          &  Trees Based on Monoidal  Categories\\
          \hline
          \textbf{Funding Organization} & National Science Foundation (NSF)\\
          \hline
          \textbf{\$ Amount Requested} & \$70,221\\
          \hline
          \textbf{Type} & External\\
          \hline
          \textbf{PI(s)} & Harley Eades III\\
          \hline
          \textbf{Beginning/Ending Dates} & March 2016 - February 2019\\
          \hline
          \textbf{Status} (Unfunded, Funded, Pending) & Funded\\
          \hline
        \end{tabular}
    \end{tabular}
    % subsection funding_(awarded_grants) (end)    
    % section scholarship (end)
\end{document}
